### 2025-04-11 multiple-regression.qmd
20250411 - moderated multiple regression

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("brms")
library("tidyverse")
library("knitr")
```

@@

diag(pred) <- 0
pred
```

@@

>>>>

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("tidyverse")
library("knitr")
```

@@

diag(pred) <- 0
```

@@

First, we mean-center the predictors.
In this case, we center the predictors around the mean of height and weight for Wide Receivers:

```{r}
player_stats_seasonal$height_centered <- player_stats_seasonal$height - mean(player_stats_seasonal$height[which(player_stats_seasonal$position == "WR")], na.rm = TRUE)
player_stats_seasonal$weight_centered <- player_stats_seasonal$weight - mean(player_stats_seasonal$weight[which(player_stats_seasonal$position == "WR")], na.rm = TRUE)
```

Then, we compute the interaction term as the multiplication of the two centered predictors:

```{r}
player_stats_seasonal$heightXweight <- player_stats_seasonal$height_centered * player_stats_seasonal$weight_centered
```

Then, we fit the moderated multiple regression model:

```{r}
moderationModel <- lm(
  fantasyPoints_transformed ~ height_centered + weight_centered + height_centered:weight_centered,
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)

summary(moderationModel)
```

This model is equivalent to the model that includes the interaction term explicitly:

```{r}
#| eval: false

moderationModel <- lm(
  fantasyPoints_transformed ~ height_centered + weight_centered + heightXweight,
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)

summary(moderationModel)
```

Now, we can visualize the interaction to understand it.
We create an interaction plot (@fig-interactionPlot) and Johnson-Neyman plot (@fig-johnsonNeymanPlot) using the `interactions` package [@R-interactions].

```{r}
#| label: fig-interactionPlot
#| fig-cap: "Interaction Plot from Moderated Multiple Regression."
#| fig-alt: "Interaction Plot from Moderated Multiple Regression."

interactions::interact_plot(
  moderationModel,
  pred = height_centered,
  modx = weight_centered)
```

```{r}
#| label: fig-johnsonNeymanPlot
#| fig-cap: "Johnson-Neyman Plot from Moderated Multiple Regression."
#| fig-alt: "Johnson-Neyman Plot from Moderated Multiple Regression."

interactions::johnson_neyman(
  moderationModel,
  pred = height_centered,
  modx = weight_centered,
  alpha = .05)
```

Here is a simple slopes analysis:

```{r}
interactions::sim_slopes(
  moderationModel,
  pred = height_centered,
  modx = weight_centered,
  johnson_neyman = FALSE)
```
